\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 paper.tex

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{makecell}
\usepackage{float}
\usepackage{placeins}

@@

\title{\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\bibitem{noVehiocles}
Department for Transport {\em Provisional Road Traffic Estimates Great Britain: October 2016-September 2017}. Department for Transport WebSite: https://www.gov.uk/government/statistics/provisional-road-traffic-estimates-great-britain-october-2016-to-september-2017.

\bibitem{distance}
Department for Transport {\em Vehicle Licensing Statistics: Quarter 3 (Jul-Sep) 2017}. Department for Transport WebSite: https://www.gov.uk/government/statistics/vehicle-licensing-statistics-july-to-september-2017.

@@

\bibitem{ShortestPath?2015}
Zhu, Shanjiang, and David Levinson. {\em Do people use the shortest path? An empirical test of Wardrop’s first principle}. PloS one 10.8 (2015): e0134322.

>>>>

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{makecell}
\usepackage{float}
\usepackage{placeins}
\usepackage{microtype}

@@

\title{\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
A. Stephen McGough\footnotemark[1]}
\date{}

@@

\bibitem{noVehiocles}
Department for Transport {\em Provisional Road Traffic Estimates Great Britain: October 2016-September 2017}. url (visited January 2017): https://www.gov.uk\-/government/statistics/provisional-road-traffic-estima\-tes-great-britain-october-2016-to-september-2017.

\bibitem{distance}
Department for Transport {\em Vehicle Licensing Statistics: Quarter 3 (Jul-Sep) 2017}. url (visited 31 January 2017): https://www.gov.uk/government/statistics\-/vehicle-licensing-statistics-july-to-september-2017.

@@

% \bibitem{ShortestPath?2015}
% Zhu, Shanjiang, and David Levinson. {\em Do people use the shortest path? An empirical test of Wardrop’s first principle}. PloS one 10.8 (2015): e0134322.
